Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2025-10-29 manuscript_latex/manuscript.tex
Update Appendix B.

Let \(\mathbf{X}\) be a feature with ordered feature values, and
\(\mathbf{Y}^\lambda =\phi^{\lambda} \left(\mathbf{X} \right)\) and
\(\mathbf{Y}^{\lambda, x_0, s} =\phi^{\lambda, x_0, s} \left(\mathbf{X} \right)\)
its transformed values using conventional and shift and scale invariant
power transformations, respectively. Since power transformations are
monotonic, \(\mathbf{Y}\) will likewise be ordered.

Below we will focus on criteria based on the empirical density function
and those based on skewness and kurtosis of the transformed featured.
Other potential criteria, such as the Shapiro-Wilk test statistic
\citet{Raymaekers2024-zf} are not investigated here. In the case of the
Shapiro-Wilk test statistic this is because of lack of scalability to
features with many (\(> 5000\)) instances, and because adapting the test
statistic to include weights is not straightforward.

@@

Here \(w_i\) are weights, and \(\mu\) and \(\sigma\) are location and
scale parameters. For non-robust power transformations, all \(w_i = 1\).
Note that this criterion is not the same as the Anderson-Darling test
statistic \citep{Anderson1952-gz}, which involves solving (or
approximating) an integral function, contains an extra scalar
multiplication term, and does not include weights. The Anderson-Darling
criterion seeks to minimise the squared Euclidean distance between the
EDF and the normal CDF, with differences at the upper and lower end of
the normal CDF receiving more weight than those at the the centre of the
CDF.

\subsubsection{Cram\'{e}r-von Mises
criterion}\label{cramer-von-mises-criterion}

The Cram\'{e}r-von Mises criterion is also based on the empirical
distribution function of \(\mathbf{X}\). We define the Cram\'{e}r-von Mises
criterion as follows:

@@

Here \(w_i\) are weights, and \(\mu\) and \(\sigma\) are location and
scale parameters. For non-robust power transformations, all \(w_i = 1\).
The criterion is similar to the Cram\'{e}r-von Mises test statistic
\citep{Cramer1928-rc, Von_Mises1928-ef}, aside from a additive scalar value and the introduction of
weights. This criterion, like the Anderson-Darling criterion, seeks to
minimise the squared Euclidean distance between the EDF and the normal
CDF. Unlike the Anderson-Darling criterion, this criterion weights all
instances equally.

For conventional power transformations with a fixed shift parameter, the
transformation \(\phi^{\lambda, x_0, s} (\mathbf{X})\) may be
substituted by \(\phi^{\lambda} (\mathbf{X})\) in the definition of the
Cram\'{e}r-von Mises criterion.

@@

For the kurtosis test statistic we first compute \citep{Anscombe1983-nz, DAgostino1990-kp}:

@@

{\centering \includegraphics[width=1\linewidth]{appendix_figure_1}

>>>>

Let \(\mathbf{X}\) be a feature with ordered feature values, and
\(\mathbf{Y}^\lambda =\phi^{\lambda} \left(\mathbf{X} \right)\) and
\(\mathbf{Y}^{\lambda, x_0, s} =\phi^{\lambda, x_0, s} \left(\mathbf{X} \right)\)
its transformed values using conventional and location- and
scale-invariant power transformations, respectively. Since power
transformations are monotonic, \(\mathbf{Y}\) will likewise be ordered.

Below we will focus on criteria based on the empirical density function
and those based on skewness and kurtosis of the transformed feature.
Other potential criteria, such as the Shapiro-Wilk test statistic
\citep{Shapiro1965-zd} are not investigated here. In the case of the
Shapiro-Wilk test statistic this is because of lack of scalability to
features with many (\(> 5000\)) instances, and because adapting the test
statistic to include weights is not straightforward.

@@

Here \(w_i\) are weights, and \(\mu\) and \(\sigma\) are location and
scale parameters. For non-robust power transformations, all \(w_i = 1\).
Note that this criterion is not the same as the Anderson-Darling test
statistic \citep{Anderson1952-gz}, which involves solving (or
approximating) an integral function, contains an extra scalar
multiplication term, and does not include weights. The Anderson-Darling
criterion seeks to minimise the squared Euclidean distance between the
EDF and the normal CDF, with differences at the upper and lower end of
the normal CDF receiving more weight than those at the centre of the
CDF.

\subsubsection{Cramér-von Mises
criterion}\label{cramuxe9r-von-mises-criterion}

The Cramér-von Mises criterion is also based on the empirical
distribution function of \(\mathbf{X}\). We define the Cramér-von Mises
criterion as follows:

@@

Here \(w_i\) are weights, and \(\mu\) and \(\sigma\) are location and
scale parameters. For non-robust power transformations, all \(w_i = 1\).
The criterion is similar to the Cramér-von Mises test statistic
\citep[\citet{Von_Mises1928-ef}]{Cramer1928-rc}, aside from an additive
scalar value and the introduction of weights. This criterion, like the
Anderson-Darling criterion, seeks to minimise the squared Euclidean
distance between the EDF and the normal CDF. Unlike the Anderson-Darling
criterion, this criterion weights all instances equally.

For conventional power transformations with a fixed shift parameter, the
transformation \(\phi^{\lambda, x_0, s} (\mathbf{X})\) may be
substituted by \(\phi^{\lambda} (\mathbf{X})\) in the definition of the
Cramér-von Mises criterion.

@@

For the kurtosis test statistic we first compute
\citep{DAgostino1990-kp, Anscombe1983-nz}:

@@

{\centering \includegraphics{manuscript_appendix_files/figure-latex/shifted-distributions-appendix-1}
